---
title: "Assignment 3: Data Visualization (incarceration)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("maps")
library("dplyr")
library("ggplot2")
library("leaflet")
library("tidyverse")
library("plotly")
```

## R Markdown

### Introduction:
This project is centered around the data on incarceration rates in the US. This
data was a bit larger then expected but after i picked my topic which is the 
difference between black and white prison population i was able to filter down 
the data, but i felt that wasn't enough so i took another look at the data again
and noticed that our own states mass incarceration rates of black people has 
increased drastically in the last several years. This became the forces of my 
first chart. I then looked at the relationship between the incarceration rates 
of black people vs whites in New York between the years 1990 and 2000 when the 
the infamous stop and frisk policy came full swing. Then to wrap things up i made 
a map that highlights the county's with the largest black prison population. The
variables i have choose to work with in my data are the total population, the total
black population and other simple ones such as year county name and state.

## My Charts:

**Chart1**:
This graph shows how the incarceration rate of black people has increased in Washington
state from 1990 to 2018. Can see that the even in our state the issue of mass incarceration
has effected the rate that black people are put in jail far surpassing the rate in which
white population in jail is increasing.

```{r chart1, echo=FALSE, warning=FALSE}
source("../source/analysis.R")
x
```
**Chart2**:
We now can take a look at how the 2 races compare in a different place such as New York.
the time period i choose to forces on now is 1990-2000 because this was the time period
in which the stop and frisk policy in New York was very popular and we can see how that 
effected the increased of the black population while the white population decreased.
```{r chart2, echo=FALSE, warning=FALSE}
y + annotate("text", x = 1992.5, y = 2000000, label = "White population")+
  annotate("text", x = 1992.5, y = 1300000, label = "Black population")
```

**Map**:
This map was made to represent the county in the us that have a larger ratio of black
inmates compared to the national average. as we take a look at the map we can clearly
see that the majority southern states have much darker tone to them indicating that 
each county in that area have more then the average ratio of black people in jail 
compared to the rest of the country
```{r map, echo=FALSE, warning=FALSE, message=FALSE}
z
```